---
title: "Rational curiosity predicts the dynamics of habituation and dishabituation in infants and adults"
author: "Your Name"
date: "2023-11-13"
bibliography: library.bib
output:
  bookdown::pdf_book:
    citation_package: biblatex
    keep_tex: true
    toc: false
    
    
---

```{r, include = FALSE}
#Load packages & datasets
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(magrittr)
library(pbkrtest)
library(xtable)

# behavioral data: infants 
exp1_infant_d <- read_csv(here("data/infants/exp1.csv"))
exp2_zoom_infant_d <- read_csv(here("data/infants/exp2_zoom.csv"))
exp2_lookit_infant_d <- read_csv(here("data/infants/exp2_lookit.csv"))
exp2_control_infant_d <- read_csv(here("data/infants/exp2_control.csv"))

# behavioral data: adults 
exp1_adult_d <- read_csv(here("data/adults/adult_exposure_duration.csv"))
exp2_adult_d <- read_csv(here("data/adults/adult_stimuli_type.csv"))

# crossvalidation results
aligned_EIG_CV <- read_csv(here('data/infants/crossvalidation/aligned_EIG_CV.csv'))
resnet50_EIG_CV <- read_csv(here('data/infants/crossvalidation/resnet50_EIG_CV.csv'))
resnet50_KL_CV <- read_csv(here('data/infants/crossvalidation/resnet50_KL_CV.csv'))
resnet50_nolearning_CV <- read_csv(here('data/infants/crossvalidation/resnet50_nolearning_CV.csv'))
resnet50_nonoise_CV <- read_csv(here('data/infants/crossvalidation/resnet50_nonoise_CV.csv'))
resnet50_surprisal_short_CV <- read_csv(here('data/infants/crossvalidation/resnet50_surprisal_short_CV.csv'))

# exp1 full data comparison 
adult_fulldata_resnet50_eig <- readRDS(here("data/adults/full_data_fit/adult_fulldata_resnet50_eig.Rds"))
adult_fulldata_resnet50_kl <- readRDS(here("data/adults/full_data_fit/adult_fulldata_resnet50_kl.Rds"))
adult_fulldata_resnet50_surprisal <- readRDS(here("data/adults/full_data_fit/adult_fulldata_resnet50_surprisal.Rds"))
adult_fulldata_resnet50_nolearning <- readRDS(here("data/adults/full_data_fit/adult_fulldata_resnet50_nolearning.Rds"))
adult_fulldata_resnet50_nonoise <- readRDS(here("data/adults/full_data_fit/adult_fulldata_resnet50_nonoise.Rds"))


infant_fulldata_resnet50_eig <- read_csv(here("data/infants/full_data_fit/infants_fulldata_resnet50_EIG.csv"))
infant_fulldata_resnet50_kl <- read_csv(here("data/infants/full_data_fit/infants_fulldata_resnet50_KL.csv"))
infant_fulldata_resnet50_surprisal <- read_csv(here("data/infants/full_data_fit/infants_fulldata_resnet50_surprisal.csv"))
infant_fulldata_resnet50_nolearning <- read_csv(here("data/infants/full_data_fit/infants_fulldata_resnet50_nolearning.csv"))
infant_fulldata_resnet50_nonoise <- read_csv(here("data/infants/full_data_fit/infants_fulldata_resnet50_nonoise.csv"))



```

```{r, include = FALSE}
# Load models
## infants 
model_1a <- readRDS(here("cached_models/infants/model_1a.rds"))
model_2a <- readRDS(here("cached_models/infants/model_2a.rds"))
model_2b <- readRDS(here("cached_models/infants/model_2b.rds"))
model_2c <- readRDS(here("cached_models/infants/model_2c.rds"))
model_2d <- readRDS(here("cached_models/infants/model_2d.rds"))
model_3a <- readRDS(here("cached_models/infants/model_3a.rds"))
model_3b <- readRDS(here("cached_models/infants/model_3b.rds"))
model_3c <- readRDS(here("cached_models/infants/model_3c.rds"))

## adults 
exp1_adult_model <- readRDS(here("cached_models/adults/exp1_adult_model.Rds"))

```


# Abstract
```{r child = "01_abstract.Rmd"}

```

# Introduction 
```{r child = "02_introduction.Rmd"}

```

# Rational Action, Nosy Choice for Habituation model
```{r child = "03_RANCH.Rmd"}

```

# RANCH predicts habituation and dishabituation in relation to exposure duration
```{r child = "04_experiment1.Rmd"}

```

# RANCH predicts stimulus similarity-based dishabituation in infants and adults
```{r child = "05_experiment2.Rmd"}

```

# General Discussion 

```{r child = "06_GD.Rmd"}

```

# Methods and Materials 

```{r child = "07_methods_model_spec.Rmd"}

```


# Supplementary Information 
```{r child = "10_supplementary.Rmd"}

```

# References 

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent