---
title: "Rational curiosity predicts the dynamics of habituation and dishabituation in infants and adults"
author: "Your Name"
date: "2023-11-13"
bibliography: library.bib
output:
  bookdown::pdf_book:
    citation_package: biblatex
    keep_tex: true
    toc: false
    
    
---

```{r, include = FALSE}
#Load packages & datasets
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(magrittr)
library(pbkrtest)
library(xtable)

# behavioral data
exp1_infant_d <- read_csv(here("data/infants/exp1.csv"))
exp2_zoom_infant_d <- read_csv(here("data/infants/exp2_zoom.csv"))
exp2_lookit_infant_d <- read_csv(here("data/infants/exp2_lookit.csv"))

# crossvalidation results
aligned_EIG_CV <- read_csv(here('data/infants/crossvalidation/aligned_EIG_CV.csv'))
resnet50_EIG_CV <- read_csv(here('data/infants/crossvalidation/resnet50_EIG_CV.csv'))
resnet50_KL_CV <- read_csv(here('data/infants/crossvalidation/resnet50_KL_CV.csv'))
resnet50_nolearning_CV <- read_csv(here('data/infants/crossvalidation/resnet50_nolearning_CV.csv'))
resnet50_nonoise_CV <- read_csv(here('data/infants/crossvalidation/resnet50_nonoise_CV.csv'))
resnet50_surprisal_short_CV <- read_csv(here('data/infants/crossvalidation/resnet50_surprisal_short_CV.csv'))

```

```{r, include = FALSE}
# Load models
model_1a <- readRDS(here("cached_models/infants/model_1a.rds"))
model_2a <- readRDS(here("cached_models/infants/model_2a.rds"))
model_2b <- readRDS(here("cached_models/infants/model_2b.rds"))
model_2c <- readRDS(here("cached_models/infants/model_2c.rds"))
model_2d <- readRDS(here("cached_models/infants/model_2d.rds"))
model_3a <- readRDS(here("cached_models/infants/model_3a.rds"))
model_3b <- readRDS(here("cached_models/infants/model_3b.rds"))
model_3c <- readRDS(here("cached_models/infants/model_3c.rds"))
```


# Abstract
```{r child = "01_abstract.Rmd"}

```

# Introduction 
```{r child = "02_introduction.Rmd"}

```

# Rational Action, Nosy Choice for Habituation model
```{r child = "03_RANCH.Rmd"}

```

# RANCH predicts habituation and dishabituation in relation to exposure duration
```{r child = "04_experiment1.Rmd"}

```

# RANCH predicts stimulus similarity-based dishabituation in infants and adults

```{r child = "05_experiment2.Rmd"}

```

# General Discussion 

```{r child = "06_GD.Rmd"}

```

# Methods and Materials 

```{r child = "07_methods_model_spec.Rmd"}

```

```{r child = "08_methods_infants.Rmd"}

```

```{r child = "09_methods_adults.Rmd"}

```

# Supplementary information 
```{r child = "10_supplementary.Rmd"}

```

# References 

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent