---
title: "00_main.Rmd"
output: html_document
date: "2023-11-13"
---

---
title: ""
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    
abstract: >

keywords: >
    psychology; cognitive development; learning

    
output: 
    cogsci2016::cogsci_paper
    
  
nocite: | 
 

final-submission: \cogscifinalcopy
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```


```{r}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(magrittr)
library(pbkrtest)
```

Load packages & datasets

```{r}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(magrittr)
library(pbkrtest)

infant_d <- read_csv(here("data/infants/infant_processed_data.csv"))
```
# Load models
```{r}

model_1a <- readRDS(here("cached_models/infants/model_1a.rds"))
model_2a<- readRDS(here("cached_models/infants/model_2a.rds"))
model_2b<- readRDS( here("cached_models/infants/model_2b.rds"))
model_2c <- readRDS( here("cached_models/infants/model_2c.rds"))
model_2d <- readRDS(here("cached_models/infants/model_2d.rds"))
model_3a <- readRDS(here("cached_models/infants/model_3a.rds"))
model_3b <- readRDS(here("cached_models/infants/model_3b.rds"))
model_3c <- readRDS( here("cached_models/infants/model_3c.rds"))

```



# Introduction 

# ```{r child = "01_introduction.Rmd"}
# ```


## Methods

```{r child = "02_methods_infants.Rmd"}
```

## Results

```{r child = "03_results_infants.Rmd"}
```

## Methods

# ```{r child = "04_experiment2_methods.Rmd"}
# ```

## Results

# ```{r child = "05_experiment2_results.Rmd"}
# 
# ```

# Discussion 

# ```{r child = "06_general_discussion.Rmd"}
# ```

# References 

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent