
```{r, include=FALSE}
# Load data for infants 

# Number of subjects
total_n_exp1 = exp1_infant_d %>% pull(unique_id) %>% unique() %>% length()

# number of subjects after exclusions
total_n_exp1_after_exclusion = exp1_infant_d %>% filter(!exclude) %>% pull(unique_id) %>% unique() %>% length()

# experiment-specific sample size
n_subject_expA = exp1_infant_d %>% filter(str_detect(unique_id, "A")) %>% pull(unique_id) %>% unique() %>% length()
n_subject_expB = exp1_infant_d %>% filter(str_detect(unique_id, "B")) %>% pull(unique_id) %>% unique() %>% length()
n_subject_expC = exp1_infant_d %>% filter(str_detect(unique_id, "C")) %>% pull(unique_id) %>% unique() %>% length()

# age and sex
mean_age_exp1 <- exp1_infant_d %>% group_by(unique_id) %>% summarize(age_in_months = mean(age)/30) %>% pull(age_in_months) %>% mean() %>% round(2)

age_sex_df_exp1 = exp1_infant_d %>% distinct(unique_id, age, sex) %>% mutate(age_in_months = age/30) 
mean_age_exp1 = age_sex_df_exp1 %>% pull(age_in_months) %>% mean() %>% round(2)
sex_exp1 = age_sex_df_exp1 %>% count(sex)

```


```{r, include=FALSE}
# Load data for adults 

# Number of subjects
n_subject_adult_exp1 <- exp1_adult_d %>% distinct(prolific_id) %>% count() %>% pull()

```

```{r eval=FALSE, include=FALSE}
## ONLY RUN IF MODELS NEED TO BE RERUN
# exclude invalid trials
exp1_infant_d %<>% filter(!exclude)

# get age
mean_age = exp1_infant_d %>% distinct(unique_id, age) %>% pull(age) %>% mean()
sd_age = exp1_infant_d %>% distinct(unique_id, age) %>% pull(age) %>% sd()

test_df = exp1_infant_d %>% filter(fam_or_test == 'test') %>% mutate(fam_duration = as.numeric(fam_duration), 
                                                                animal = as.factor(animal), 
                                                                centered_age = (age - mean_age) / sd_age)


# checking for non-linearity model
model_1a <- lmer(log(LT) ~ poly(fam_duration,2) * test_type + block_num + (1 | unique_id), data = test_df)

# fam pref (EXPLORATORY)
model_2a <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration == 1))

model_2b <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration == 3))

model_2c <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration == 4))

# fam pref pre-registered
model_2d <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration <= 4 & fam_duration != 0))

# dishabituation
model_3a <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration == 8))

model_3b <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration == 9))

model_3c <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration >= 8))

saveRDS(model_1a, here("cached_models/infants/model_1a.rds"))
saveRDS(model_2a, here("cached_models/infants/model_2a.rds"))
saveRDS(model_2b, here("cached_models/infants/model_2b.rds"))
saveRDS(model_2c, here("cached_models/infants/model_2c.rds"))
saveRDS(model_2d, here("cached_models/infants/model_2d.rds"))
saveRDS(model_3a, here("cached_models/infants/model_3a.rds"))
saveRDS(model_3b, here("cached_models/infants/model_3b.rds"))
saveRDS(model_3c, here("cached_models/infants/model_3c.rds"))

```

```{r, eval=FALSE, include=FALSE}
# results figure

#Results figure
data = read_csv(here('data/results_plots/exp1_data_plot.csv')) %>% mutate(tt = tolower(tt))
sim_infants = read_csv(here('data/results_plots/exp1_infant_sim_plot.csv')) %>% mutate(test_type = tolower(test_type))
sim_adults = read_csv(here('data/results_plots/exp1_adult_sim_plot.csv')) %>% mutate(trial_type = tolower(trial_type))

facet_labels <- tibble(
  type = c("EIG","KL","Surprisal", "No Learning", "No Noise"),
  label = c("EIG","KL","Surprisal", "No Learning", "No Noise"), 
  x = c(6, 6, 6, 6, 6), 
  y = c(1, 1, 1, 1, 1),
) %>% mutate(across(type, ~factor(., levels=c("EIG","KL","Surprisal", "No Learning", "No Noise")))) 


adult_bp <- data %>% 
  filter(group == "Adults") %>% 
  ggplot(aes(x=x, y=y, group=tt, color = tt)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               position = position_dodge(width = .3)) +
  stat_summary(geom = "line",
               position = position_dodge(width = .3)) + 
  theme_few(20) + 
  ylab("Looking time (sec)") +
  xlab("Trial Number") + 
  ggthemes::scale_color_solarized(name = "Trial type") +
  theme(legend.position = "none")

adult_simulation_plot <- ggplot() +
  theme_few() +
  stat_summary(
    data = sim_adults, 
    aes(x = trial_number, y = scaled_samples/1000, color = trial_type),
    fun.data = mean_cl_boot, na.rm = TRUE)+
   stat_summary(
    data = sim_adults, 
    aes(x = trial_number, y = scaled_samples/1000, color = trial_type),
    fun.data = mean_cl_boot, na.rm = TRUE, 
    geom = "line") + 
  geom_text(data = facet_labels, aes(x = 6, label = label), y = Inf, vjust = 2)+ 
  facet_wrap(~factor(type, levels=c("EIG","KL","Surprisal", "No Learning", "No Noise"))) +
  theme(
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 15),
    legend.position = c(0.85, 0.25), 
    legend.background = element_rect(fill = "white", colour = NA) 
  ) + 
  ylab("") + 
  xlab("") + 
  guides(color=guide_legend(title="Trial type")) +
  theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()) + 
  scale_color_manual(values = c("familiar" = "#268bd2", "novel" = "#cb4b16"))


y_intercept_baseline = data %>% filter(x == 0) %>% pull(y) %>% mean()
  
infant_bp <- data %>% mutate(tt = ifelse(x == 0, 'baseline', tt)) %>%
  filter(group == "Infants (7 - 9 months)") %>% 
  ggplot(aes(x=x, y=y, group=tt, color = tt)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               position = position_dodge(width = .3)) +
  stat_summary(geom = "line",
               position = position_dodge(width = .3)) +
  theme_few(20) + 
  ylab("Looking time (sec)") +
  xlab("Prior exposures") + 
  ggthemes::scale_color_solarized(name = "Trial type") +
  theme(legend.position = "none") + 
  scale_color_manual(values = c("familiar" = "#268bd2", "novel" = "#cb4b16", "baseline" = "grey")) + 
  scale_x_continuous(breaks =c(0,1,2,3,4,6,8,9)) + 
  geom_hline(yintercept = y_intercept_baseline, linetype = "dashed", color = 'grey')

infant_simulation_plot <- ggplot() +
  theme_few() +
  stat_summary(
    data = sim_infants, 
    aes(x = fam_duration, y = scaled_samples, color = test_type),
    fun.data = mean_cl_boot, na.rm = TRUE)+
   stat_summary(
    data = sim_infants, 
    aes(x = fam_duration, y = scaled_samples, color = test_type),
    fun.data = mean_cl_boot, na.rm = TRUE, 
    geom = "line") + 
  geom_text(data = facet_labels, aes(x = 5, label = label), y = Inf, vjust = 2)+ 
  scale_x_continuous(breaks =c(0,1,2,3,4,6,8,9)) + 
  facet_wrap(~factor(type, levels=c("EIG","KL","Surprisal", "No Learning", "No Noise")))+
  theme(
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 15),
    legend.position = c(0.85, 0.25), 
    legend.background = element_rect(fill = "white", colour = NA) 
  ) + 
  ylab("") + 
  xlab("") + 
  guides(color=guide_legend(title="Trial type")) +
  theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()) + ylim(c(5,28)) + 
  scale_color_manual(values = c("familiar" = "#268bd2", "novel" = "#cb4b16"))
  

infant_res_fig <- plot_grid(infant_bp, infant_simulation_plot, rel_widths = c(1, 1))
adult_res_fig <- plot_grid(adult_bp, adult_simulation_plot, rel_widths = c(1, 1))

ggsave(here('figs/infant_exp1_res.png'),infant_res_fig, width = 10, height = 5)
ggsave(here('figs/adult_exp1_res.png'),adult_res_fig, width = 10, height = 5)

```

```{r, include=FALSE}
# clean up stats models
model_1a_df <- tidy(model_1a) %>% mutate(across(where(is.numeric) & !c("p.value"), ~ round(., 2))) %>% mutate(p.value = round(p.value, 3))
model_2a_df <- tidy(model_2a) %>% mutate(across(where(is.numeric) & !c("p.value"), ~ round(., 2))) %>% mutate(p.value = round(p.value, 3))
model_2b_df <- tidy(model_2b) %>% mutate(across(where(is.numeric) & !c("p.value"), ~ round(., 2))) %>% mutate(p.value = round(p.value, 3))
model_2c_df <- tidy(model_2c) %>% mutate(across(where(is.numeric) & !c("p.value"), ~ round(., 2))) %>% mutate(p.value = round(p.value, 3))
model_2d_df <- tidy(model_2d) %>% mutate(across(where(is.numeric) & !c("p.value"), ~ round(., 2))) %>% mutate(p.value = round(p.value, 3))
model_3a_df <-tidy(model_3a) %>% mutate(across(where(is.numeric) & !c("p.value"), ~ round(., 2))) %>% mutate(p.value = round(p.value, 3))
model_3b_df <-tidy(model_3b) %>% mutate(across(where(is.numeric) & !c("p.value"), ~ round(., 2))) %>% mutate(p.value = round(p.value, 3))
model_3c_df <-tidy(model_3c) %>% mutate(across(where(is.numeric) & !c("p.value"), ~ round(., 2))) %>% mutate(p.value = round(p.value, 3))

exp1_adult_model_df <- exp1_adult_model %>%  tidy() %>%  mutate_if(is.numeric, round, 2)

```


```{r eval=FALSE, include=FALSE}
# Set up adult model 

exp1_adult_model_d <-  exp1_adult_d %>% mutate(is_first_trial = trial_number == 1, 
                        block_number = block_id + 1)

# m0 <- lmer(log(total_rt) ~ trial_number + is_first_trial + trial_number * trial_type + log(block_number) + (trial_number * trial_type | prolific_id) + (is_first_trial + trial_number | prolific_id), data = exp1_adult_model_d)

exp1_adult_model <- lmer(log(total_rt) ~ trial_number + is_first_trial + trial_number * trial_type + log(block_number) + (1| prolific_id), data = exp1_adult_model_d)

saveRDS(exp1_adult_model, here("cached_models/adults/exp1_adult_model.Rds"))
```


```{r, include=FALSE}

# Comparing the linking hypotheses 
adult_best_full_resnet50_eig <- adult_fulldata_resnet50_eig %>% arrange(mean_rmse) %>% head(1) %>% mutate_if(is.numeric, round, 2)
adult_best_full_resnet50_kl <- adult_fulldata_resnet50_kl %>% arrange(mean_rmse) %>% head(1)%>% mutate_if(is.numeric, round, 2)
adult_best_full_resnet50_surprisal <- adult_fulldata_resnet50_surprisal %>% arrange(mean_rmse) %>% head(1)%>% mutate_if(is.numeric, round, 2)
adult_best_full_resnet50_nolearning <- adult_fulldata_resnet50_nolearning %>% arrange(mean_rmse) %>% head(1)%>% mutate_if(is.numeric, round, 2)
adult_best_full_resnet50_nonoise <- adult_fulldata_resnet50_nonoise %>% arrange(mean_rmse) %>% head(1) %>% mutate_if(is.numeric, round, 2)

infant_best_full_resnet50_eig <- infant_fulldata_resnet50_eig %>% arrange(mean_rmse) %>% head(1) %>% mutate_if(is.numeric, round, 2)
infant_best_full_resnet50_kl <- infant_fulldata_resnet50_kl %>% arrange(mean_rmse) %>% head(1)%>% mutate_if(is.numeric, round, 2)
infant_best_full_resnet50_surprisal <- infant_fulldata_resnet50_surprisal %>% arrange(mean_rmse) %>% head(1) %>% mutate_if(is.numeric, round, 2)
infant_best_full_resnet50_nolearning <- infant_fulldata_resnet50_nolearning %>% arrange(mean_rmse) %>% head(1)%>% mutate_if(is.numeric, round, 2)
infant_best_full_resnet50_nonoise <- infant_fulldata_resnet50_nonoise %>% arrange(mean_rmse) %>% head(1) %>% mutate_if(is.numeric, round, 2)

```


The models in Figure \@ref(fig:conceptual) make contrasting predictions with regard to the effect of increasing prior exposure on looking times. To directly test these  predictions, we collected looking time data from both infants and adults in an experiment where we varied cumulative exposure to a familiar stimulus, and measured subsequent looking time to a novel or familiar stimulus. We then let RANCH ``see'' the same stimulus sequences used in our behavioral experiments and compared our model's behavior to that of humans.

## Behavioral experiments

### Infant experiment 

We tested infants in a novel experimental paradigm in which exposure duration to the familiar stimulus was manipulated in a within-subject design \@ref(fig:design) (Experiment 1, Infants). Each infant saw six blocks. In each block there was an familiarization phase and a test trial. During the familiarization phase, one animal (designated the familiar stimulus) was presented 1 to 9 times. Next, infants' looking time was measured on a test trial. The test trial showed either the familiar stimulus, or a novel animal. We ran three versions of this experiment, each with three different numbers of familiarization events. We tested a combined sample of `r total_n_exp1` 7-10 month old infants, with `r n_subject_expA` infants in Exp 1A (0, 4 or 8 familiarization events), `r n_subject_expB` infants in Exp 1B (1, 3 or 9 familiarization events) and `r n_subject_expC` infants in Exp 1C (2, 4 or 6 familiarization events; total n=`r total_n_exp1`, $M_{age}$=`r mean_age_exp1` months, `r sex_exp1$n[sex_exp1$sex == 'F']` female).


### Adult experiment 

We ran a self-paced looking time experiment on Prolific, collecting data from `r n_subject_adult_exp1` adult participants \@ref(fig:design) (Experiment 1, Adults). Stimuli used in the adult experiment were drawn from the same set used in the infant experiment. During the experiment, participants were asked to watch sequences of stimuli at their own pace, and they could press a key to proceed to the next stimulus whenever they wanted to. The time between the onset of the stimulus and the key press was used as a proxy for looking time. Each sequence began with a familiar stimulus repeating 1 to 10 times, followed by either the same familiar or a novel stimulus. 


### Modeling Procedure

RANCH received the CNN-derived stimulus embeddings as input, presented in sequences mirroring the structure of in our infant and adult experiments (\@ref(fig:design)). To simulate a block of the infant experiment, the model was first presented with the "familiar" stimulus. For each stimulus, the model took 5 samples each and then moved on to the next stimulus. This phase was designed to be to the familiarization phase infants went through, since during the familiarization phase infants had no control over the progression of the stimulus sequence. After the familiarization phase, the model was presented with the test trial, which was either familiar or novel. We used the number of samples the model took on this test trial as a proxy for infant looking time. To simulate the self-paced adult experiment, we computed the number of samples taken by RANCH on every trial in each stimulus sequence.


```{r design, echo=FALSE, fig.width=20, fig.height=14, fig.cap="Experimental design for Experiments 1 and 2, infants and adults: Experiment 1 varied exposure to a stimulus and measured looking to familiar or novel stimuli. Experiment 2 varied how the familiar stimulus was violated, by changing the pose, identity, number or animacy of the stimulus. Infants had fixed prior exposure durations (5 sec per exposure) and looking was measured until a 2-second lookaway. Adults responded on each trial via a keypress to continue to the next trial."}
img <- png::readPNG("figs/design_fig.png")
grid::grid.raster(img)
```

## Behavioral and model results

The paradigm successfully captured habituation in both infants and adults. In infants, as the number of trials in exposure increased, the looking time at the familiar stimulus in the test trials decreased ($\beta$ = `r filter(model_1a_df, term == "poly(fam_duration, 2)1")$estimate`; *SE* = `r filter(model_1a_df, term == "poly(fam_duration, 2)1")$std.error`; *t* = `r filter(model_1a_df, term == "poly(fam_duration, 2)1")$statistic`; *p* < 0.001). Infants clearly dishabituated on trials longer exposures (8 exposures: $\beta$ = `r filter(model_3a_df, term == "test_typenov")$estimate`; *SE* = `r filter(model_3a_df, term == "test_typenov")$std.error`; *t* = `r filter(model_3a_df, term == "test_typenov")$statistic`; *p* < 0.001, 9 exposures: $\beta$ = `r filter(model_3b_df, term == "test_typenov")$estimate`; *SE* = `r filter(model_3b_df, term == "test_typenov")$std.error`; *t* = `r filter(model_3b_df, term == "test_typenov")$statistic`; *p* < 0.001). The adult experimental paradigm also successfully captured habituation and dishabituation (Trial number: $\beta$ = `r filter(exp1_adult_model_df, term == "trial_number")$estimate`; Trial Type: $\beta$ = `r filter(exp1_adult_model_df, term == "trial_typedeviant")$estimate`; Both *SE* < 0.001; Both *p* < 0.001). We found no evidence for familiarity preferences or non-linearities in the shape of the dishabituation curve in infants or adults (cf. Figure \@ref(fig:conceptual)A&B).

RANCH predicted habituation and dishabituation in both infants and adults. To compare model samples to looking times, we fit a linear model adjusting the number of samples by an intercept and a scaling factor. We then computed the root mean squared error (RMSE) between the scaled model results and the looking time data. To avoid overfitting on these scaling parameters and the free parameters that we searched over, we used K-fold cross-validation, computing the average RMSE across held-out samples. This procedure was conducted separately for both infant and adult data. 


```{r xtable, results='asis', echo=FALSE, message=FALSE}

#table for CV stats
CV_table = tibble(`Linking Hypothesis` =  c("EIG", "KL", "Surprisal", "No learning", "No noise"))

CV_table = CV_table %>% mutate(`Infants: Mean RMSE` = c(mean(infant_resnet50_EIG_CV$rmse),                                                                                            mean(infant_resnet50_KL_CV$rmse),
                                                        mean(infant_resnet50_surprisal_short_CV$rmse), 
                                                        mean(infant_resnet50_nolearning_CV$rmse),
                                                        mean(infant_resnet50_nonoise_CV$rmse)), 
                               `Infants: Best RMSE` = c(min(infant_resnet50_EIG_CV$rmse), 
                                                        min(infant_resnet50_KL_CV$rmse),
                                                        min(infant_resnet50_surprisal_short_CV$rmse),
                                                        min(infant_resnet50_nolearning_CV$rmse),
                                                        min(infant_resnet50_nonoise_CV$rmse)),
                                `Adults: Mean RMSE` = c(mean(adult_kfold_resnet50_eig$mean_rmse),
                                                        mean(adult_kfold_resnet50_kl$mean_rmse),
                                                        mean(adult_kfold_resnet50_surprisal$mean_rmse),
                                                        mean(adult_kfold_resnet50_nolearning$mean_rmse),
                                                        mean(adult_kfold_resnet50_nonoise$mean_rmse)),
                                `Adults: Best RMSE` = c(min(adult_kfold_resnet50_eig$mean_rmse),
                                                        min(adult_kfold_resnet50_kl$mean_rmse),
                                                        min(adult_kfold_resnet50_surprisal$mean_rmse),
                                                        min(adult_kfold_resnet50_nolearning$mean_rmse),
                                                        min(adult_kfold_resnet50_nonoise$mean_rmse)))

knitr::kable(as.matrix(CV_table %>% as.data.frame() %>% mutate_if(is.numeric, round, digits=3)),
                      caption = "Cross-validated RMSE across linking hypotheses and lesioned models. Mean RMSE is averaged across all parameter values, best RMSE is the single best-performing parameter set", format = "latex") %>% kable_styling(latex_options = "scale_down") %>% row_spec(0,bold=TRUE)
             
```

## Comparison with alternative linking hypotheses 

EIG is the optimal method for making sampling decisions [@lindley1956measure]. We compared this method to decision-making metrics proposed in prior literature including Kullback-Leibler divergence (KL-divergence) and surprisal. KL-divergence measures the information gained when one's beliefs are updated, effectively quantifying "learning progress", while surprisal captures how inconsistent incoming information is with prior expectations. Both have been shown to be associated with infants’ looking behaviors [@kidd2012goldilocks; @poli2020infants]. We then repeated the cross-validation process using these linking hypotheses and compared the model’s performance based on the parameter that provides the best average fits to the test sets according to RMSE. Out of the three linking hypotheses, we found that EIG and KL-divergence were comparable to each other but surprisal-based RANCH performed worse in both populations (Table \@ref(tab:xtable)). 

## Comparison with lesioned model 

We tested the importance of two of RANCH's key assumptions by creating lesioned models. One assumes each perceptual sample is noiseless ("No noise"), and the other assumes the sampling decision was random instead of based on the learning model ("No learning"). Both lesioned models provided poor fits to the behavioral datasets (Table \@ref(tab:xtable)). Both the noisy perception assumption and the learning assumption appear to be critical to RANCH's performance.


## Parameter Interpretation / Developmental Comparison

One advantage of RANCH is the interpretability of its parameters. Beyond finding that RANCH’s fit to the data is robust across parameters, we can also ask which specific parameters maximize that fit. In particular, comparing the best fitting parameters between infants and adults could provide insights into the origin of the developmental differences in behavior (see ‘Joint Scaling’ under Methods for technical details). When investigating which parameters were most influential in achieving better fit, we found that $\sigma_\epsilon$ played a key role in improving fit. A high $\sigma_\epsilon$ improved fit to the infant data, but a low $\sigma_\epsilon$ improved fit to the adult data (Figure \@ref(fig:parameter-interpretation)). Conceptually, $\sigma_{\epsilon}$ represents an agent's beliefs about how much noise there is in their own perceptual input, suggesting that infants' learning behavior in our task was adjusted to higher perceptual noise. 

## Discussion 

Using within-subjects measurements of looking time, we examined the sensitivity of looking to familiar vs. novel stimuli as a function of prior exposure. We did not find evidence for non-linearities predicted by prior models (Fig. \@ref(fig:conceptual)A & \@ref(fig:conceptual)B), and instead found that habituation and dishabituation followed monotonic trends as predicted by RANCH (Fig. \@ref(fig:conceptual)C). 

We next test whether RANCH’s can make predictions in a novel dataset.

```{r infant-exp1-res,echo=FALSE,fig.width=20, fig.height=10, fig.cap="Experiment 1: Infant and RANCH simulations (different linking hypotheses and lesioned models). The x-axes show the number of prior exposures shown to infants and RANCH before measuring looking time / number of samples on the test trial, which was novel or familiar. The y-axes show the mean looking time in seconds for the behavioral panel, and the scaled model samples for RANCH. The scaling procedure was applied to each linking hypotheses/lesioned model separately. Error bars show the standard error of the mean."}
img <- png::readPNG("figs/infant_exp1_res.png")
grid::grid.raster(img)
```

```{r adult-exp1-res, echo=FALSE, fig.width=20, fig.height=10, fig.cap="Experiment 1: Adult and RANCH behavior (different linking hypotheses and lesioned models). For adults and the corresponding RANCH simulations, looking time was measured on every trial, shown on the x-axes. The y-axes show the mean looking time in seconds for the behavioral panel, and the scaled model samples for RANCH. Error bars show the standard error of the mean."}
img <- png::readPNG("figs/adult_exp1_res.png")
grid::grid.raster(img)
```
