
```{r, include=FALSE}
# Load data

# Number of subjects
total_n = exp1_infant_d %>% pull(unique_id) %>% unique() %>% length()

# number of subjects after exclusions
total_n_after_exclusion = exp1_infant_d %>% filter(!exclude) %>% pull(unique_id) %>% unique() %>% length()

# experiment-specific sample size
n_subject_expA = exp1_infant_d %>% filter(str_detect(unique_id, "A")) %>% pull(unique_id) %>% unique() %>% length()
n_subject_expB = exp1_infant_d %>% filter(str_detect(unique_id, "B")) %>% pull(unique_id) %>% unique() %>% length()
n_subject_expC = exp1_infant_d %>% filter(str_detect(unique_id, "C")) %>% pull(unique_id) %>% unique() %>% length()

# age and sex
mean_age <- exp1_infant_d %>% group_by(unique_id) %>% summarize(age_in_months = mean(age)/30) %>% pull(age_in_months) %>% mean() %>% round(2)

age_sex_df = exp1_infant_d %>% distinct(unique_id, age, sex) %>% mutate(age_in_months = age/30) 
mean_age = age_sex_df %>% pull(age_in_months) %>% mean() %>% round(2)
sex = age_sex_df %>% count(sex)

```



```{r eval=FALSE, include=FALSE}
## ONLY RUN IF MODELS NEED TO BE RERUN
# exclude invalid trials
exp1_infant_d %<>% filter(!exclude)

# get age
mean_age = exp1_infant_d %>% distinct(unique_id, age) %>% pull(age) %>% mean()
sd_age = exp1_infant_d %>% distinct(unique_id, age) %>% pull(age) %>% sd()

test_df = exp1_infant_d %>% filter(fam_or_test == 'test') %>% mutate(fam_duration = as.numeric(fam_duration), 
                                                                animal = as.factor(animal), 
                                                                centered_age = (age - mean_age) / sd_age)


# checking for non-linearity model
model_1a <- lmer(log(LT) ~ poly(fam_duration,2) * test_type + block_num + (1 | unique_id), data = test_df)

# fam pref (EXPLORATORY)
model_2a <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration == 1))

model_2b <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration == 3))

model_2c <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration == 4))

# fam pref pre-registered
model_2d <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration <= 4 & fam_duration != 0))

# dishabituation
model_3a <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration == 8))

model_3b <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration == 9))

model_3c <- lmer(log(LT) ~ test_type + block_num + (1 | unique_id), data = test_df %>% filter(fam_duration >= 8))

saveRDS(model_1a, here("cached_models/infants/model_1a.rds"))
saveRDS(model_2a, here("cached_models/infants/model_2a.rds"))
saveRDS(model_2b, here("cached_models/infants/model_2b.rds"))
saveRDS(model_2c, here("cached_models/infants/model_2c.rds"))
saveRDS(model_2d, here("cached_models/infants/model_2d.rds"))
saveRDS(model_3a, here("cached_models/infants/model_3a.rds"))
saveRDS(model_3b, here("cached_models/infants/model_3b.rds"))
saveRDS(model_3c, here("cached_models/infants/model_3c.rds"))

```

```{r, include=FALSE}
# clean up stats models
model_1a_df <- tidy(model_1a) %>% mutate_if(is.numeric, round, 2)
model_2a_df <- tidy(model_2a) %>% mutate_if(is.numeric, round, 2)
model_2b_df <- tidy(model_2b) %>%  mutate_if(is.numeric, round, 2)
model_2c_df <- tidy(model_2c) %>%  mutate_if(is.numeric, round, 2)
model_2d_df <- tidy(model_2d) %>%  mutate_if(is.numeric, round, 2)
model_3a_df <-tidy(model_3a) %>%  mutate_if(is.numeric, round, 2)
model_3b_df <-tidy(model_3b) %>%  mutate_if(is.numeric, round, 2)
model_3c_df <-tidy(model_3c) %>%  mutate_if(is.numeric, round, 2)
```



A key difference between the competing models in Figure \@ref(fig:conceptual) is their prediction with regard to the effect of familiarity on looking time. To address this, we collected looking time data from both infants and adults in an experiment where we varied exposure duration to a familiar stimulus, and measured subsequent looking time to a novel vs. familiar stimulus. We then let RANCH "see" the same stimuli and procedure used in our behavioral experiments and evaluated our model’s behavior against the behavioral datasets.

## Behavioral experiments

### Infant experiment 

We tested infants in a novel experimental paradigm in which exposure duration to the stimuli were manipulated in a within-subject design \@ref(fig:design) (Experiment 1, Infants). Each infant saw six blocks. In each block there was an familiarizaiton phase and a test trial. During the familiarization, infants were presented with one stimulus, repeated 0 to 9 times. After the familiarization, infants’ looking time was measured on a test trial. The test trial showed either the same stimulus as the preceding trials, or a new stimulus. We ran three versions of this experiment, each with three different familiarization durations. We tested a combined sample of `r total_n` 7-10 month old infants, with `r n_subject_expA` infants in Exp 1A (0, 4 or 8 repetitions), `r n_subject_expB` infants in Exp 1B (1, 3 or 9 repetitions) and `r n_subject_expC` infants in Exp 1C (2, 4 or 6 repetitions; total n=`r total_n`, $M_{age}$=`r mean_age` months, `r sex$n[sex$sex == 'F']` female).


### Adult experiment 

We ran a self-paced looking time paradigm experiment on Prolific, collecting data from XXXX adult participants \@ref(fig:design) (Experiment 1, Adults). The stimuli used in the adult experiment are drawn from the same stimuli set used in the infant experiment. During the experiment, participants were asked to watch sequences of animations at their own pace, and they could press a key to proceed to the next trial whenever they wanted to. The time between the onset of the stimulus and the key press was used as a proxy for looking time. Each sequence of animations has two stimuli: the familiar stimulus and the novel stimulus. The familiar stimulus repeated over and over again within a sequence, whereas the novel stimulus only appeared once and it appeared at either the second, the fourth, or the sixth position in the sequence. 


### Modeling Procedure

The overall modeling strategy is for RANCH to ‘see’ the experiment the same way as the participants do. RANCH learned from the embeddings derived from the stimuli used in the experiments, and the modeling procedure mirrored the experimental set-up used in the infants experiment and adult experiment respectively (\@ref(fig:design)). 

To simulate the infant experiment, the model was first presented with a series of repeating stimuli. For each stimulus, the model took 5 samples each and then moved on to the next stimulus. This phase is similar to the exposure phase infants went through, since during the exposure phase infants had no control over the progression of the stimuli sequence. After the familiarization sequence, the model was presented with the test trial, which either has a novel stimulus or a familiar stimulus (i.e. the repeated stimulus). The number of samples the model took on this test trial was the “looking time” that the model produced.  

To simulate the self-paced adult experiment, RANCH makes decisions on how many samples to take on every trial, until the end of the sequence. As in the adult experiment, the sequence has a familiar stimulus that repeats throughout the sequence, and a novel stimulus that appears once. The model therefore predicts looking times to each stimulus in the sequence. 


```{r design, echo=FALSE, fig.width=20, fig.height=14, fig.cap="Experimental design"}
img <- png::readPNG("figs/design_fig.png")
grid::grid.raster(img)
```

## Evaluating model with behavioral results 


The paradigm successfully captured habituation in both infants and adults. In infants, as the number of trials in exposure increased, the looking time at the familiar stimulus in the test trials decreased ($\beta$ = `r filter(model_1a_df, term == "poly(fam_duration, 2)1")$estimate`; *SE* = `r filter(model_1a_df, term == "poly(fam_duration, 2)1")$std.error`; *t* = `r filter(model_1a_df, term == "poly(fam_duration, 2)1")$statistic`; *p* < 0.001). We also found evidence for infants’ dishabituation: looking time for the novel test trials was longer than the familiar trial after long exposures (after 8 repetitions: $\beta$ = `r filter(model_3a_df, term == "test_typenov")$estimate`; *SE* = `r filter(model_3a_df, term == "test_typenov")$std.error`; *t* = `r filter(model_3a_df, term == "test_typenov")$statistic`; *p* < 0.001, after 9 repetitions: $\beta$ = `r filter(model_3b_df, term == "test_typenov")$estimate`; *SE* = `r filter(model_3b_df, term == "test_typenov")$std.error`; *t* = `r filter(model_3b_df, term == "test_typenov")$statistic`; *p* < 0.001). Likewise, we also found that adult experimental paradigm successfully captures habituation and dishabituation (STATS). We found no evidence for familiarity preferences or non-linearities in the shape of the dishabituation curve in infants or adults (cf. \@ref(fig:conceptual)A&B).

RANCH predicted habituation and dishabituation in both infants and adults. We evaluated each parameter set’s performance by running a K-fold crossvalidation test. At each fold, we fit a linear model predicting the looking time data in the fold. We then used the coefficients and the intercepts from the fitted model to scale the model results to the rest of the behavioral data. We compute RMSE and the Pearson’s r between the scaled model results and the test set. This process is repeated for each fold and for each parameter setting. For infants, we used K = 2 due to the data sparsity. For adults, we used K = 10. The K-fold validation suggests that our model performance is largely robust across parameters (Table ??). 


```{r xtable, results='asis', echo=FALSE}

#table for CV stats
CV_table = tibble(`Linking Hypothesis` =  c("EIG", "KL", "Surprisal", "No learning", "No noise"))

CV_table = CV_table %>% mutate(`Infants: Mean RMSE` = c(mean(resnet50_EIG_CV$rmse), mean(resnet50_KL_CV$rmse), mean(resnet50_surprisal_short_CV$rmse), mean(resnet50_nolearning_CV$rmse), mean(resnet50_nonoise_CV$rmse))) %>% mutate(`Infants: Best RMSE` = c(min(resnet50_EIG_CV$rmse), min(resnet50_KL_CV$rmse), min(resnet50_surprisal_short_CV$rmse), min(resnet50_nolearning_CV$rmse), min(resnet50_nonoise_CV$rmse)), `Adults: Mean RMSE` = , `Adults: Best RMSE` = )

table <- xtable(as.matrix(CV_table %>% as.data.frame() %>% mutate_if(is.numeric, round, digits=3)), caption = "Table 1: Crossvalidation results")

print.xtable(table, include.rownames = FALSE, comment = FALSE,
              size="\\fontsize{8pt}{9pt}\\selectfont")

```

## Comparison with alternative linking hypotheses 

We also compared the performance of RANCH when using EIG, which is the fully rational linking hypothesis, to other, proxy-based linking hypothesis used in prior literature: Kullback-Leibler divergence (KL-divergence) and surprisal. KL-divergence measures the information gained when one's beliefs are updated, effectively quantifying 'learning progress', while surprisal captures how inconsistent incoming information is with prior expectations. Both have been shown to be associated with infants’ looking behaviors (CITE, CITE). We then compared the model’s performance based on the parameter that provides the best fits to the full dataset. Out of the three linking hypotheses, we found that EIG and KL-divergence were comparable to each other (Infants: STATS; Adults: STATS). But surprisal-based RANCH performed worse in both populations (Infants: STATS; Adults: STATS). We also found that the noisy perception assumption and the learning assumptions were both critical to RANCH’s performance.

## Comparison with lesioned model 

We also examined the importance of RANCH’s key assumption. To do so, we created two lesioned models: one model assumes each perceptual sample is noiseless (“No noise model”), and the other model assumes the sampling decision was random instead of based on the learning model (“No learning model”). Both lesioned models provided poor fits for the behavioral datasets (Table \@ref(tab:xtable)). 

## Parameter Interpretation / Developmental Comparison

One advantage of RANCH is the interpretability of its parameters. Beyond finding that RANCH’s fit to the data is robust across parameters, we can also ask which specific parameters maximize that fit. In particular, comparing the best fitting parameters between infants and adults could provide insights into the origin of the developmental differences in behavior (see ‘Joint Scaling’ under Methods for technical details). When investigating which parameters were most influential in achieving better fit, we found that sd_epsilon played a key role in improving fit. Conceptually, $\sigma_{\epsilon}$ represents an agent's beliefs about how much noise there is in their own perceptual input. We found that this value tends to be high for infants, and low for adults ([SUPPLEMENTARY FIGURES WITH HISTOGRAM OF RMSE COLORED BY PARAMETER VALUES]). 

## Discussion 

Through within-subjects measurements of looking time, we examined the sensitivity of looking to familiar vs. novel stimuli as a function of prior exposure. We did not find evidence for non-linearities predicted by prior models (Fig. \@ref(fig:conceptual)A & \@ref(fig:conceptual)B), and instead found that habituation and dishabituation followed monotonic trends as predicted by RANCH (Fig. \@ref(fig:conceptual)C). 

We next turn to test RANCH’s ability to make predictions in a novel dataset. 
