
## Deriving predictions for Goldilocks model

Below is an illustration of how predictions for a habituation/dishabituation experiment were derived for the Goldilocks model. In all cases, as infants get familiarized, the surprisal of the familiar stimulus goes down, and the surprisal of the novel stimulus has to go up, so that probabilities assigned to events add up to 1. Depending on the initial surprisal of the familiarization stimulus, there are three different trajectories of preferences to novel vs. familiar stimuli as a function of prior exposure: 1) If initial surprisal is below the optimal level to maximize attention, the model predicts an increase, and then a decrease in novelty preferences. 2) If initial surprisal is at the optimal level, then no preference is predicted, assuming a symmetric U-shape. 3) If initial surprisal is higher than optimal surprisal, the model predicts an increasing, and then decreasing familiarity preference. 

```{r goldilocks-explanation, echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=5, set.cap.width=T, num.cols.cap=1, fig.cap="Illustration of how predictions from the Goldilocks model in Fig. 1 were derived."}

img <- png::readPNG("figs/goldilocks_explanation.png")
grid::grid.raster(img)

```


## Parameter robustness

To evaluate RANCH’s robustness to different parameters, we tested its fit for all possible parameter settings. Performance across the 162 parameter settings was relatively stable, yielding a moderate range RMSE values for infants and adults across linking hypotheses. In both cases most parameter settings outperformed the fit achieved by baseline models (Table \@ref(tab:xtable)). The distribution of RMSE values across parameter settings are shown in the histograms below (Figure \@ref(fig:parameter-robustness)).

```{r parameter-robustness, echo=FALSE, warning=FALSE, message=FALSE, fig.pos="H", fig.width=20, fig.height=7, fig.cap="Histograms of RMSE for different linking hypotheses show that RANCH is largely robust to variations in parameters."}

# infants
infant_eig_hist = infant_resnet50_EIG_CV %>% ggplot(aes(x = rmse)) + geom_histogram() + xlab('RMSE') + theme_classic(15) + labs(title = "Infants: EIG") 
infant_kl_hist = infant_resnet50_KL_CV %>% ggplot(aes(x = rmse)) + geom_histogram() + xlab('RMSE') + theme_classic(15) + labs(title = "KL") + theme(plot.title = element_text(hjust = 0.5))
infant_surprisal_hist = infant_resnet50_surprisal_short_CV %>% ggplot(aes(x = rmse)) + geom_histogram() + xlab('RMSE') + theme_classic(15) + labs(title = "Surprisal") + theme(plot.title = element_text(hjust = 0.5)) 

# adults
adult_eig_hist = adult_kfold_resnet50_eig %>% ggplot(aes(x = mean_rmse)) + geom_histogram() + xlab('RMSE') + theme_classic(15) + labs(title = "Adults: EIG")
adult_kl_hist = adult_kfold_resnet50_kl %>% ggplot(aes(x = mean_rmse)) + geom_histogram() + xlab('RMSE') + theme_classic(15) + labs(title = "KL") + theme(plot.title = element_text(hjust = 0.5))
adult_surprisal_hist = adult_kfold_resnet50_surprisal %>% ggplot(aes(x = mean_rmse)) + geom_histogram() + xlab('RMSE') + theme_classic(15)  + labs(title = "Surprisal") + theme(plot.title = element_text(hjust = 0.5))


combined_plot <- ggarrange(
  ggarrange(infant_eig_hist, infant_kl_hist, infant_surprisal_hist, ncol = 3),
  ggarrange(adult_eig_hist, adult_kl_hist, adult_surprisal_hist, ncol = 3),
  nrow = 2
) + theme_classic(20)

combined_plot

```

## Scaling the embedding space

In order to achieve sensible results, it was important to bring the stimulus embeddings in line with the approximation grid used for inference. Below we show what happens embeddings exceeded or came close to the edges of the our approximation grids. In Experiment 1, unscaled embeddings resulted in a reversal of background vs. deviant model samples, such that the model takes more samples from the background than the deviant. In Experiment 2, unscaled embeddings resulted in an unintuitive ordering which is not in line with the embedding distances (Figure \@ref(fig:embedding_distances)). 

```{r wrong-scaling, echo=FALSE, warning=FALSE, message=FALSE, fig.width=20, fig.height=7, fig.cap="The effect of scaling on model results. A) Experiment 1 with unscaled embeddings results in a reversal of background vs. deviant. B) Experiment 2 with unscaled embeddings results in an unintuitive ordering."}

# load unscaled stuff
exp1_unscaled = read_csv(here('data/infants/unscaled_model_data/exp1_resnet50_unscaled.csv'))
exp2_unscaled = read_csv(here('data/infants/unscaled_model_data/exp2_resnet50_unscaled.csv'))

exp1_plot <- exp1_unscaled %>% ggplot(aes(x = fam_duration, y = sample_n_mean, color = violation_type)) +
 stat_summary(fun.data = "mean_cl_boot") + theme_classic(20) + xlab('Exposure duration') + ylab("Model samples") + theme(legend.position = "none") + labs(title = "Exp1 unscaled", tag = "A")

exp2_plot <- exp2_unscaled %>% ggplot(aes(x = trial_type, y = mean_sample, color = trial_type)) + stat_summary() + theme_classic(20) + theme(legend.position = "none") + ggtitle('Exp2 unscaled') + xlab("Violation type") + ylab("Model samples") + labs(title = "Exp2 unscaled", tag = "B")

library("gridExtra")

grid.arrange(exp1_plot, exp2_plot, ncol = 2, nrow = 1) 

```

## Developmental comparison of parameter fits
```{r, include=FALSE, message=FALSE, warning=FALSE}
joint_scaling_fits = read_csv('data/joint_scaling_fits.csv')

param_info <- read_csv(here("data/param_info.csv"))

best_params = joint_scaling_fits %>% arrange(rmse) %>% first()

#  best fits
infant_best_id = best_params$p_i
infant_best_params = param_info %>% filter(param_id == infant_best_id)

adult_best_fit = best_params$p_a
adult_best_params = param_info %>% filter(param_id == adult_best_fit)
```
A naive approach to comparison parameter fits between infants and adults would be the following: After joint scaling, pick the set of parameters for adults and infants that together minimize RMSE. If we do this, we obtain the following parameter sets: 

infants: $\nu$= `r infant_best_params$V_prior`, $\alpha$= `r infant_best_params$alpha_prior`, $\beta$= `r infant_best_params$beta_prior`, $\sigma_\epsilon$= `r infant_best_params$sd_epsilon`, $\sigma_\epsilon$= `r infant_best_params$sd_epsilon`, $EIG_{env}$= `r infant_best_params$world_EIGs`

adults: $\nu$= `r adult_best_params$V_prior`, $\alpha$= `r adult_best_params$alpha_prior`, $\beta$= `r adult_best_params$beta_prior`, $\sigma_\epsilon$= `r adult_best_params$sd_epsilon`, $\sigma_\epsilon$= `r adult_best_params$sd_epsilon`, $EIG_{env}$= `r adult_best_params$world_EIGs`

If we compare these two sets of parameters to each other, and interpret these differences, we may come to the following conclusion: RANCH fits best when infants' $\sigma_\epsilon$ is higher than that of adults, and $\beta_prior$ is higher than that of adults, suggesting that infants both expect their perception to have more noise, and that infants have more prior uncertainty about the size of the standard deviation.

However, a direct comparison between these parameter sets does not give insight into the relative stability of RANCH's fit to the data if we change any of these parameters: It may be that if a parameter was slightly different, it would not make a big difference for model fit. 

In order to investigate this, we want to also check the sensitivity of the model fit to changes in the parameters. To do so, we plot RMSE histograms colored by the value of a certain parameter, from a certain age group. Here we see that the overall modes of the RMSE histograms are dominated by `world EIG`, likely because this parameter is the main threshold that can account for the difference in scale between infant and adult looking times. However, of the other parameters, we see that RMSE only shows sensitivity to $\sigma_\epsilon$. Other parameters that are different between the best fits do not show this sensitivity. We therefore conclude that the main interpretable parameter difference is in $\sigma_\epsilon$, the learner's noise prior, being higher in infants than in adults.


```{r parameter-interpretation, fig.env = "figure", fig.width=10, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Histograms of model fit colored by priors. Results suggest that when the learner's noise is high, RANCH fits infant data better."}
library(ggplot2)
library(gridExtra)
library(dplyr)

fit_df_infants = joint_scaling_fits %>% 
  rename(param_id = p_i) %>% 
  left_join(param_info %>% select(param_id, V_prior, alpha_prior, beta_prior, sd_epsilon, world_EIGs), by = "param_id") %>%  
  mutate(across(-c(rsquared, rmse), as.factor))

plot_1a = ggplot(fit_df_infants, aes(x = rmse, fill = beta_prior)) + 
  geom_histogram() + 
  ggtitle(expression(Colored~by~Infant~beta)) +
  scale_fill_discrete(name = expression(beta)) + ylab("")

plot_1b = ggplot(fit_df_infants, aes(x = rmse, fill = sd_epsilon)) + 
  geom_histogram() + 
  ggtitle(expression(Colored~by~Infant~sigma[epsilon])) +
  scale_fill_discrete(name = expression(sigma[epsilon])) + ylab("")

plot_1c = ggplot(fit_df_infants, aes(x = rmse, fill = V_prior)) + 
  geom_histogram() + 
  ggtitle(expression(Colored~by~Infant~nu)) +
  scale_fill_discrete(name = expression(nu)) + ylab("")

fit_df_adults = joint_scaling_fits %>% 
  rename(param_id = p_a) %>% 
  left_join(param_info %>% select(param_id, V_prior, alpha_prior, beta_prior, sd_epsilon, world_EIGs), by = "param_id") %>%  
  mutate(across(-c(rsquared, rmse), as.factor)) 

plot_2a = ggplot(fit_df_adults, aes(x = rmse, fill = beta_prior)) + 
  geom_histogram() + 
  ggtitle(expression(Colored~by~Adult~beta)) +
  scale_fill_discrete(name = expression(beta)) + ylab("")

plot_2b = ggplot(fit_df_adults, aes(x = rmse, fill = sd_epsilon)) + 
  geom_histogram() + 
  ggtitle(expression(Colored~by~Adult~sigma[epsilon])) +
  scale_fill_discrete(name = expression(sigma[epsilon])) + ylab("")

plot_2c = ggplot(fit_df_adults, aes(x = rmse, fill = V_prior)) + 
  geom_histogram() + 
  ggtitle(expression(Colored~by~Adult~nu)) +
  scale_fill_discrete(name = expression(nu)) + ylab("")

grid.arrange(
  plot_1a + theme(legend.position = "none"), 
  plot_1b + theme(legend.position = "none"), 
  plot_1c + theme(legend.position = "none"), 
  plot_2a + theme(legend.position = "bottom"), 
  plot_2b + theme(legend.position = "bottom"), 
  plot_2c + theme(legend.position = "bottom"), 
  ncol = 3, nrow = 2
)

```

## Embedding distances of different violations categories, by embedding model

Below we plot the embedding distances of the different violations. The lines connect a single stimulus, and the y-axis represents the embedding distances to all the stimuli that would constitute a certain violations. For example, for a single animal stimulus, the y-value for 'animacy' corresponds to the distance between the single animal and all the single fruit/vegetable stimuli.  

```{r embedding-distances, echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=5, set.cap.width=T, num.cols.cap=1, fig.cap="Embedding distances of different violation types for 1) a base ResNet50 model, 2) a perceptually aligned embedding model (Lee, 2022) and 3) a ResNet50 model trained on SAYCAM data (Orhan et al., 2020)"}

img <- png::readPNG("figs/embedding_distances.png")
grid::grid.raster(img)

```


## Control experiment for Experiment 2 in infants

Given that the familiarization trial always consisted of a single animal, it is possible that differences in looking times during test trials of different types were a result of differences in interest in the stimuli themselves (e.g. our inanimate stimuli may have been intrinsically more interesting than our animals). To test whether infants were differently interested in our stimuli due to intrinsic stimulus properties, we ran a control experiment in which we showed infants our different stimulus types without any prior familiarization. Infants saw three types of stimuli for as long as they wanted, up to 60 seconds: single animals, fruits/vegetables, or pairs of animals. There were six trials per session, so infants saw two of each stimulus type.

```{r, include=FALSE}

exp2_control_infant_d$trial_type =  relevel(as.factor(exp2_control_infant_d$trial_type), ref = "single animal")
model_control = lmer(log(LT) ~ trial_type + log(block_num) + (1|subject_num), data = exp2_control_infant_d)

tidy_control_model = tidy(model_control) %>% mutate(across(where(is.numeric) & !c("p.value"), ~ round(., 2))) %>% mutate(p.value = round(p.value, 3))

```

We found no evidence for differences in baseline interest in our stimuli. as neither looking to inanimate stimuli nor animal pairs differed significantly from looking to single animals (inanimate stimuli: $\beta$ = `r filter(tidy_control_model, term == "trial_typeveggie")$estimate`; *SE* = `r filter(tidy_control_model, term == "trial_typeveggie")$std.error`; *t* = `r filter(tidy_control_model, term == "trial_typeveggie")$statistic`; *p* = `r  filter(tidy_control_model, term == "trial_typeveggie")$p.value`; animal pairs: $\beta$ = `r filter(tidy_control_model, term == "trial_typeanimal pair")$estimate`; *SE* = `r filter(tidy_control_model, term == "trial_typeanimal pair")$std.error`; *t* = `r filter(tidy_control_model, term == "trial_typeanimal pair")$statistic`; *p* = `r  filter(tidy_control_model, term == "trial_typeanimal pair")$p.value`). Therefore, the fact that animacy violations elicited the strongest dishabituation in the main Experiment 2 suggests that this resulted from the transition from animate to inanimate stimuli, rather than enhanced interest in inanimate stimuli themselves.

```{r, include=FALSE, message=FALSE, warning=FALSE}

control_plot <- ggplot(exp2_control_infant_d %>% filter(!exclude, LT > 2) %>% mutate(trial_type = factor(trial_type, levels = c("single animal", "animal pair", "veggie"))), aes(x=trial_type, y=LT)) + geom_jitter(width = 0.03, alpha = 0.2) + stat_summary(fun.data = "mean_cl_boot", geom = "line", position = position_dodge(width = .1))  + 
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", position = position_dodge(width = .1), size = 1.2) + xlab('') + ylab('Looking time (sec)') + theme_grey(base_size = 20) + 
  theme(strip.text.x = element_text(size = 20, colour = "black")) + coord_cartesian(ylim = c(0,50)) + theme_bw(20)

ggsave(here('figs/control_exp.png'), control_plot, width = 10, height = 5)

```

```{r control-exp, fig.env = "figure", fig.width=10, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Control experiment for experiment 2, checking for baseline differences in interest. No significant differences were found."}

img <- png::readPNG("figs/control_exp.png")
grid::grid.raster(img)

```

